Distributional State Aggregation

### 2020-03-17 minutia/paper/paper.tex
paper: aggregation part completed

    \section{State Aggregation}
    Value function approximation alleviates the computational hurdle of a large state-space problem.
    We introduce an approximate policy iteration method to solve an aggregate problem.
    State aggregation is an approximation approach to make a problem more tractable by a reduction in dimensionality in
    state space \footnote{aggre
    gation in action space although is possible, has less significance comparatively.}.
    State aggregation, in particular, is a parametric feature-based approximation where the features are membership
    functions of 0-1 form.
    Aggregation groups similar states together, so called representative states, which lets the \textit{aggregate}
    problem to be solved by an exact method.
    The computed value function from the exact solution of the aggregate problem can be then used in the original
    problem.

@@

    \subsection{Aggregation}
    The original states with the closest \textit{calculated} values forgather to build aggregate states.
    For this purpose, state values are clustered by K-means analysis to calculate the relevant aggregate states.
    State aggregation merge similar transitions based on a triple $<s, s', a>$ where $s$ indicates the starting state,
    $s'$ is the ending state, and the take action in that transition represented by $a$.
    In the process of stacking similar transitions, we here presume all inbound transitions as outbound transition of
    the ending state.
    This assumption render all transitions as outbound ones.

>>>>

    \section{State Aggregation}
    Value function approximation alleviates the computational hurdle of a large state-space problem.
    We introduce an approximate policy iteration method to solve an aggregate problem.
    State aggregation is an approximation approach to make a problem more tractable by a reduction in dimensionality in
    state space \footnote{aggregation in action space although is possible, has less significance comparatively.}.
    State aggregation, in particular, is a parametric feature-based approximation where the features are membership
    functions of 0-1 form.
    Aggregation groups similar states together, so called representative states, which lets the \textit{aggregate}
    problem to be solved by an exact method.
    The computed value function from the exact solution of the aggregate problem can be then used in the original
    problem.

@@

    \subsection{Aggregation}
    The original states with the closest \textit{calculated} values forgather to build aggregate states.
    For this purpose, state values are clustered by K-means analysis to calculate the relevant aggregate states.
    State aggregation merge similar transitions based on a triple $<s, s', a>$ where $s$ indicates the starting state,
    $s'$ is the ending state, and the take action in that transition represented by $a$.
    In the process of stacking similar transitions, we here presume all inbound transitions as outbound transition of
    the ending state.
    This assumption render all transitions as outbound ones, therefore we assign the average probability as the
    transition probability in the aggregate model.
